\Title

### 2021-01-26 manuscript/manuscript.tex
Start reviewing the Australia application

\begin{equation}
    \left[
      \mathbf{B}\trans \mathbf{W} \mathbf{B} + \lambda \mathbf{I}
    \right]
    \hat{\mathbf{m}} =
    \mathbf{B}\trans\mathbf{W}
    \mathbf{d}^o.
    \label{eq:least_squares_solution}
\end{equation}

@@

In the following sections, we will test the effectiveness and trade-offs of
each of these strategies on synthetic data.

@@

\section{Tests on synthetic data}

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/synthetic-survey-layouts.pdf}
    \caption{
        Maps of the observation locations and gravity values for the synthetic
        ground and airborne surveys.
        (a)~Horizontal position and height of the ground survey points.
        (b)~Synthetic gravity data calculated on the ground survey points with
        added pseudo-random Gaussian noise.
        (c)~Horizontal position and height of the airborne survey points.
        (d)~Synthetic gravity data calculated on the airborne survey points
        with added pseudo-random Gaussian noise.
        Heights are given in meters above the zero height plane.
    }
    \label{fig:synthetic-layouts}
\end{figure*}

\begin{figure}
    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
    \caption{
        Pseudo-color map of the target grid of synthetic gravity data. The grid
        is composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
        with a spacing of \TargetSpacing{}. The grid height is \TargetHeight{}
        above the zero height plane.
    }
    \label{fig:synthetic-target}
\end{figure}

We have used synthetic gravity datasets to test the interpolation accuracy of
the difference horizontal and vertical source distribution strategies as well
as the gradient-boosted equivalent source method.
To generate the data, we created a model that is made out of \NPrisms{}
right-rectangular prisms, distributed on a region of
\ModelEasting{}$\times$\ModelNorthing{} with depths varying between
\ModelDepth{} and zero.
The density contrast of prisms ranges from \ModelMinDensity{} to
\ModelMaxDensity{}.
The model includes prisms of different shapes, sizes, and depths to create
gravity disturbances with a variety of wavelengths.

We created two synthetic datasets from the model, one simulating a ground
survey and another an airborne acquisition (Fig.~\ref{fig:synthetic-layouts}).
To create the synthetic ground survey, we selected measurement positions from a
portion of a public domain dataset for Southern Africa, available through the
NOAA National Centers for Environmental Information (NCEI)\footnote{
\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}
(last accessed 25 January 2020)}.
For the synthetic airborne survey, we used a portion of the Great Britain Aeromagnetic
Survey acquired by Hunting Geology and Geophysics Ltd and Canadian Aeroservices
Ltd between 1955 and 1965 and made publicly available by the
British Geological Survey (BGS)\footnote{
\url{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}
(last accessed 25 January 2020)}.
In both cases, we rescaled the horizontal coordinates of each survey portion to
span an area of \SurveyEasting{}$\times$\SurveyNorthing{}, matching the model
dimensions.
The ground survey contains \GroundSurveyPoints{} observations distributed at
heights between \GroundSurveyMinHeight{} and \GroundSurveyMaxHeight{}
(Fig.~\ref{fig:synthetic-layouts}a).
The airborne survey has \AirborneSurveyPoints{} observations at heights between
\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
(Fig.~\ref{fig:synthetic-layouts}c).

The vertical component of the gravitational acceleration generated by the
model was computed  using the method of \citet{nagy2000, nagy2002}
with recent modifications by \citet{fukushima2020},
as implemented in the open-source software Harmonica \citep{harmonica}.
We generated a \emph{target grid} of
\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
\TargetSpacing{} and located \TargetHeight{} above the zero height plane
(Fig.~\ref{fig:synthetic-target}) to serve as a reference when calculating the
interpolation error.
We then generated synthetic ground (Fig.~\ref{fig:synthetic-layouts}b) and
airborne (Fig.~\ref{fig:synthetic-layouts}d) data to which we added
pseudo-random Gaussian noise with zero mean and \SurveyNoise{} standard
deviation.

\subsection{Source distribution strategies}

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/ground_survey_differences.pdf}
    \caption{
        Pseudo-color maps of the differences between the target grid and the
        interpolated synthetic ground survey data produced by each source
        distribution strategy.
        The black dots represent the horizontal location of the synthetic data
        points. The RMS error and total number of equivalent sources is
        reported for each strategy at the top of the respective maps.
    }
    \label{fig:ground-survey-differences}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/airborne_survey_differences.pdf}
    \caption{
        Pseudo-color maps of the differences between the target grid and the
        interpolated synthetic airborne survey data produced by each source
        distribution strategy.
        The black dots represent the horizontal location of the synthetic data
        points. The RMS error and total number of equivalent sources is
        reported for each strategy at the top of the respective maps.
    }
    \label{fig:airborne-survey-differences}
\end{figure*}

We investigated the effect of different strategies for distributing the
equivalent sources horizontally and vertically on interpolation accuracy.
To do this, we used the damped least-squares solution described in
Section~\ref{sec:eql_inversion} (without gradient boosting) to interpolate the
synthetic datasets (Fig.~\ref{fig:synthetic-layouts}) and compared the results
against the target grid (Fig.~\ref{fig:synthetic-target}).
This process was repeated for each combination of horizontal layout
(sources-below-data and block-averaged-sources) and depth type (constant,
relative, and variable) and for regular-grid sources with a constant depth,
totalling 7 different combinations.

Each source distribution strategy requires certain hyper-parameters to be
chosen in order to build the set of point sources.
For example, using a constant depth needs the definition of the depth and using
block-average-sources requires the definition of the block size.
The predictive capabilities of the equivalent sources depend on the choice of
these hyper-parameters.
To ensure that our comparisons are fair, we perform an exhaustive search over
combinations of hyper-parameter values (including the damping parameter from
Eq.~\ref{eq:misfit}) to obtain the best prediction that can be achieved by each
source distribution strategy.
Here, the best prediction is defined as the one that minimizes the root
mean-square error (RMS) between interpolated values and the target grid
(Fig.~\ref{fig:synthetic-target}).
The parameter values used in these searches and the one producing the smallest
RMS error are outlined in Tables~\ref{tab:parameters-ground-survey}
and~\ref{tab:parameters-airborne-survey}.

Figures~\ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences} show the differences between the
target grid and the best prediction achieved by each source distribution
strategy for the ground and airborne synthetic surveys, respectively.
For the synthetic ground survey, the horizontal layouts produced similar RMS
values of approximately \SI{0.8}{\mgal} regardless of the depth type, with the
exception of the regular-grid layout which produced a larger RMS of
\SI{\BestGroundGridSourcesConstantDepthRms{}}{\mgal}.
The differences between the target grid and the interpolated values are larger
in regions of poor data coverage.
Edge effects are present for all strategies but are noticeably smaller for the
combination of block-averaged-sources with a variable depth based on the
nearest neighbour distance.
For the synthetic airborne survey, all strategies (including the regular-grid)
produced similar RMS errors of approximately \SI{0.3}{\mgal}.
The maps of the differences between the target grid and interpolation results
are visually indistinguishable from each other.

\subsection{Window size and overlap in gradient boosting}

We assessed the trade-offs in interpolation accuracy and computation time of
the gradient-boosted equivalent sources algorithm as a function of the two key
controlling factors: the window size and the window overlap.
The comparisons were performed against a regular least-squares solution
(Eq.~\ref{eq:least_squares_solution}) using the synthetic airborne data
(Fig.~\ref{fig:synthetic-layouts}c-d) .
To avoid biasing the results, we used the same locations of equivalent sources
for both the regular and gradient-boosted interpolations, namely
block-averaged-sources with a block size of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter} and a
relative depth of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}.

\subsubsection{Window size}
\label{sec:window_size}

The size of the windows controls the size of the Jacobian matrices
$\tilde{\mathbf{A}}_k$ by limiting the number of data points and equivalent
sources used in each step of the gradient-boosting algorithm
(Alg.~\ref{alg:gradient_boosting_window}).
Thus, using smaller windows will reduce the total amount of computer memory
required to estimate the source coefficients.
Nevertheless, smaller windows may produce less accurate interpolations by
failing to achieve the global minimum of the goal function in
Eq.~\ref{eq:misfit}.
The window size might also impact the computation time in non-intuitive ways
since smaller windows generate smaller least-squares problems but also require
more gradient-boosting iterations.

We calculated the interpolation RMS error and computation time for a fixed
window overlap of 50\% and several window sizes.
To avoid any biases introduced by the shuffling of windows, the calculations
were repeated using different seeds for the pseudo-random number generator used
in the shuffling.
Figs.~\ref{fig:gradient-boosted-comparison}a and
\ref{fig:gradient-boosted-comparison}c show the RMS error and computation time
required for estimating the source coefficients, respectively, as a function of
the window size.

The results show that the interpolation RMS error for gradient-boosting is
generally larger than the error for regular equivalent sources.
The error decreases asymptotically to within $\sim 40\%$ of the regular
equivalent sources for windows with an area greater than $\sim 35\%$ of the
survey area.
The computation time similarly decreases with window size, with the
gradient-boosting being generally faster than the regular equivalent sources
for windows with an area greater than $\sim 20\%$ of the survey area.
As the window size increases, both RMS error and computation time appear to
stabilize to nearly constant levels.

\subsubsection{Amount of overlap}

@@

We have also computed the fitting time ratio for each overlap, in a similar way
we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-comparison}d).

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-comparisons.pdf}
    \caption{
        Comparison of the interpolation RMS error and computation time for
        regular least-squares equivalent sources (orange dashed lines) and
        gradient-boosted equivalent sources (blue dots and error bars).
        Both methods used the same source positions (block-averaged sources
        with a relative depth).
        Window sizes are given as a fraction of the survey area (e.g., 1
        represents a window with the same area as the survey) and window
        overlap is given as a fraction of the window size (e.g., 0.5 equals
        50\% overlap).
        Computation time refers to the time required to estimate the source
        coefficients and is reported as a ratio between the gradient-boosted
        and the regular equivalent sources.
        For gradient-boosting, the RMS errors and computation times are the
        means (error bars represent 1 standard deviation) of results using
        different seeds for the pseudo-random number generator.
        (a)~RMS error between the target grid and interpolation results and
        (b)~computation time as a function of window size.
        (c)~RMS error between the target grid and interpolation results and
        (d)~computation time as a function of window overlap.
}
    \label{fig:gradient-boosted-comparison}
\end{figure*}

@@

\section{Gridding Australia gravity data}

@@

Our final goal is to show how gradient-boosted equivalent sources can be used
to interpolate a very large dataset of gravity data into a regular grid.
We selected a compilation of gravity surveys over Australia made by
\citet{wynne2018}.
It consists in more than 1.7 million data points that cover most part of the
Australia territory obtained through observations on ground.
First we compute the gravity disturbance by removing the normal gravity from
the observed gravity data (Fig.~\ref{fig:australia}).
The normal gravity is computed on each observation point through the
closed-form formula given by \citet{ligotze2001} and using the WGS84 ellipsoid
as reference.
Then we obtain planar coordinates of the observation points by applying
a Mercator projection.

We start the interpolation process by defining a set of block-averaged sources
at a relative depth of \AustraliaEqlDepth{} and a block spacing of
\SI{1.8}{\kilo\meter}.
These parameters create \AustraliaEqlNSources{}~point sources.
The choice of the block spacing must be done taking into account the desired
resolution of the final grid.
If the grid will have a much higher resolution than the block spacing, the
equivalent sources will not be able to reproduce the high frequency components
of the data.
Therefore we recommend setting a block spacing that matches the resolution of
the final grid.
In this case we will generate a regular grid with a resolution of 1~arc-minute,
which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.

@@

\section{Discussion}

\subsection{Location of sources}

Window size:

In comparison with the non-boosted equivalent sources, we can see that the
gradient-boosted ones produce slightly less accurate results due to not being
able to achieve the global minimum of the least-squares problem, but they
perform faster.
The reduction of the accuracy might be due to an oversimplification of the
least-squares problem, and the increase of the computational time might be
generated by the great number of iterations required to fit the sources.
As the windows gets larger, the accuracy starts increasing because more data
points are included into the fitting process of the source coefficients, while
the fitting process takes less time due to a reduction of the number of
iterations.
When using gradient-boosted equivalent sources we can conclude that we want to
maximize the window size as much as possible.
The only limitation to do so is to generate Jacobian matrices larger than the
available memory.
Therefore we recommend using the largest window that generates Jacobian
matrices that could fit in the available memory.

@@

We are indebted to the developers and maintainers of the open-source software
without which this work would not have been possible.
The synthetic airborne survey was based upon the Great Britain aeromagnetic
data, reproduced with the permission of the British Geological Survey
\textcopyright{} UKRI.
All rights reserved.

>>>>

\begin{equation}
    \left[
      \mathbf{B}\trans \mathbf{W} \mathbf{B} + \lambda \mathbf{I}
    \right]
    \hat{\mathbf{m}} =
    \mathbf{B}\trans\mathbf{W}
    \mathbf{d}^o.
\end{equation}

@@

In the following sections, we will test the effectiveness and trade-offs of
each of these strategies on synthetic data.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Comparison of source distributions}

The combination of the three source layouts with the three strategies to define
the depth of the sources define seven different source distributions (see
Table~\ref{tab:source-distributions}).
The \emph{grid sources} is only compatible with the \emph{constant depth}
scheme if no further information is provided.

\begin{table*}
    \centering
    \caption{
        Source distributions as combinations of source layouts and depth
        strategies.
    }
    \label{tab:source-distributions}
    \begin{tabular}{lccc}
        & Source below data & Block averaged sources & Grid sources \\ \hline
        Constant depth & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
        Relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
        Variable depth & $\checkmark$ & $\checkmark$ & $\times$     \\
    \end{tabular}
\end{table*}

Our first goal is to to compare the performance of all source distributions
from Table~\ref{tab:source-distributions} when predicting harmonic field data
using the equivalent sources technique.
To do so we have created a synthetic model made out of prisms of different
shape and density contrasts.
The gravitational effect of this synthetic model have been computed on
a regular grid (\emph{target} grid) at a constant height and on two different
set of observation points that we will call \emph{synthetic surveys}: a ground
and an airborne survey.
The data from each synthetic survey is interpolated on the points of the
\emph{target} grid and then scored against its values.
We can then quantitatively compare how accurate is each source distribution at
predicting unobserved data on each synthetic survey and quantify the
computational load needed to do it.

\subsection{Synthetic Model}

%Describe forward model made out of prisms.
%Show prisms model?

The synthetic model is made out of \NPrisms{} prisms distributed on a region of
\ModelEasting{}$\times$\ModelNorthing{} between \ModelDepth{} deep and the zero
height plane.
Density contrast of prisms range from \ModelMinDensity{} and
\ModelMaxDensity{}.
We built deep big and thin shallow prisms for creating gravity anomalies with
long and short wavelengths, respectively.

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on a regular grid of
\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
\TargetSpacing{} located \TargetHeight{} above the zero height plane
(Fig.~\ref{fig:target-grid}), using \citet{nagy2000} and \citet{nagy2002}.
We will refer to this grid as the \emph{target} grid in the future.

\begin{figure}
    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
    \caption{
        Target grid. Gravitational effect of synthetic model on a regular grid
        composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
        with a spacing of \TargetSpacing{} located \TargetHeight{} above the
        zero height plane.
    }
    \label{fig:target-grid}
\end{figure}

\subsection{Synthetic Surveys}

In order to compare the predictive capabilities of each source distribution
under on different surveys, we created a ground and an airborne \emph{synthetic
surveys}.
For creating the synthetic ground survey we selected a portion of the Southern
Africa Gravity Data available through the
\href{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}{NOAA website}.
For the airborne survey we used a portion of the Great Britain Aeromagnetic
Survey acquired by Hunting Geology and Geophysics Ltd and Canadian Aeroservices
Ltd between 1955 and 1965 and made available by the
\href{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}{
British Geological Survey (BGS)
}.

On both cases we selected only a portion of the survey and rescaled it to span
on an area of \SurveyEasting{}$\times$\SurveyNorthing{}.
The ground survey is composed by \GroundSurveyPoints{} observation points
distributed at heights ranging between \GroundSurveyMinHeight{} and
\GroundSurveyMaxHeight{} (Fig.~\ref{fig:synthetic-ground-survey}(a)).
While the airborne survey has \AirborneSurveyPoints{} points at heights between
\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
(Fig.~\ref{fig:synthetic-ground-survey}(a)).

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on both surveys.
Some Gaussian noise (with standard deviation of \SurveyNoise{}) has been added
to the effect of the synthetic model to simulate acquisition errors
(Figs.~\ref{fig:synthetic-ground-survey}(b)
and~\ref{fig:synthetic-airborne-survey}(b)).

\begin{figure}
    \includegraphics[width=\linewidth]{figs/ground-survey.pdf}
    \caption{
        Synthetic ground survey.
        (a)~Location of observation points. Altitude given in meters above the
            zero height plane.
        (b)~Vertical component of gravity acceleration generated by the
            synthetic model plus Gaussian noise on the ground survey
            observation points.
    }
    \label{fig:synthetic-ground-survey}
\end{figure}

\begin{figure}
    \includegraphics[width=\linewidth]{figs/airborne-survey.pdf}
    \caption{
        Synthetic airborne survey.
        (a)~Location of observation points. Altitude given in meters above the
            zero height plane.
        (b)~Vertical component of gravity acceleration generated by the
            synthetic model plus Gaussian noise on the airborne survey
            observation points.
        Based upon the Great Britain aeromagnetic data, with the permission of
        the British Geological Survey.
    }
    \label{fig:synthetic-airborne-survey}
\end{figure}

\subsection{Comparisons}

Each source distribution from Table~\ref{tab:source-distributions} needs
certain parameters in order to build the set of point sources.
The prediction capabilities of the source distribution depends on the choice of
these parameters.
For example, locating the sources beneath the data points at constant depth
needs the definition of the \emph{depth} parameter.
If the sources are set too close to the data points, the source distribution
it's very likely to over-fit the data: the measured field will be recovered, but
the predictions on unobserved locations will be very inaccurate.
Another parameter that plays an important role on the predictive capabilities
of the sources is the \emph{damping}.

On real world scenarios, choosing the values of the parameters is a challenging
task: it's not easy to determine the accuracy of the predictions without
knowing the true value of the field on unobserved locations.
This problem can be solved through cross-validation.
When working with a synthetic model, the situation is different: we can compute
the true values of harmonic field generated by the synthetic model on any
point.
Therefore, interpolating the observed data on the same points of the
\emph{target} grid and then scoring the prediction against the true values of
the \emph{target} grid constitutes an objective way to measure the predictive
accuracy of the source distribution.

In order to compare the predictive capabilities of each source distribution we
perform a parameter search to obtain the best prediction that can be achieved
by each one of them.
For each source distribution we proposed different values for each parameter
(see Tables~\ref{tab:parameters-ground-survey}
and~\ref{tab:parameters-airborne-survey}).
These parameters values are combined obtaining several \emph{set of
parameters}.
We use each set of parameters to create the sources, fit their coefficients
through least-squares and predict the field on the same points of the
\emph{target} grid.
We then \emph{score} the prediction by computing the root mean square (RMS)
between the prediction and the true values of the \emph{target} grid.
Finally, we obtain the \emph{best prediction} for each source distribution as
the one that achieves the lowest RMS.
This process is carried out on both ground and airborne synthetic surveys.
See Algorithm~\ref{alg:source_distributions_comparison} for a concise
representation of it.

\begin{algorithm}[!h]
  \DontPrintSemicolon
  \setstretch{1.5}

  define possible values for each parameter
  \;

  generate each possible combination of parameters values: obtain several
  \emph{sets of parameters}
  \;

  \For{each set of parameters}{

    select the $M$ locations of the equivalent sources
    \;

    estimate the source coefficients
    \;

    predict field values on target grid points
    \;

    calculate the RMS between the predictions and the target grid
    \;
  }

  the best set of parameters produces the smallest RMS
  \;

  \BlankLine
  \setstretch{1}
  \caption{Algorithm for estimating the best prediction using synthetic data.}
  \label{alg:source_distributions_comparison}
\end{algorithm}

Tables~\ref{tab:parameters-ground-survey}
and~\ref{tab:parameters-airborne-survey} also show the parameter combination
that produces the best prediction for each source distribution and its
corresponding RMS score, for both ground and airborne synthetic surveys,
respectively.
Figures~\ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences} show the differences between the
target grid and the best prediction achieved by each source distribution, for
both ground and airborne synthetic surveys, respectively.

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/ground_survey_differences.pdf}
    \caption{
        Differences between gravitational effects measured on the target grid
        and the ones produced by the best prediction made by each source
        distribution based on the synthetic ground survey.
    }
    \label{fig:ground-survey-differences}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/airborne_survey_differences.pdf}
    \caption{
        Differences between gravitational effects measured on the target grid
        and the ones produced by the best prediction made by each source
        distribution based on the synthetic airborne survey.
    }
    \label{fig:airborne-survey-differences}
\end{figure*}

\subsection{Discussion}

@@

\section{Performance of gradient-boosted equivalent sources}

Our second goal is to assess the accuracy of the predictions achieved by the
gradient boosting algorithm while registering its performance by comparison
with the non-boosted equivalent sources.

\subsection{Window size}
\label{sec:window_size}

One factor that plays an important role on the performance of the gradient
boosted equivalent sources is the size of the overlapping windows used to create
each set of equivalent sources.
The size of the windows controls the size of the Jacobian matrices
$\tilde{\mathbf{A}_k}$: smaller windows create smaller Jacobian matrices.
Thus, using smaller windows will reduce the amount of computer memory needed to
fit the source coefficients.
Nevertheless, smaller windows may produce less accurate predictions because
their inability to achieve the global minimum of the misfit from
equation~\ref{eq:misfit-unscaled}.
Besides, the window size might also impact on the computation time needed to
fit the source coefficients: smaller windows will generate simpler least-square
problems which are easier to solve, but they will also create more iterations.

We want to assess how the size of the overlapping windows impacts both the
accuracy of the predictions and the computation time needed to fit the source
coefficients in comparison with the performance of the non-boosted equivalent
sources.

We applied the gradient boosted equivalent sources to interpolate the synthetic
airborne survey on the same points of the target grid.
We selected several window sizes to assess how accuracy and performance depend
on that variable.
For each window size we gridded the synthetic data using block-averaged sources
with a spacing of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
a relative depth of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}, an overlap
of 50\%, and with different values of damping.
Then we compared the resulting interpolations with the target grid in order to
get the best prediction for each window size and the damping value used to
obtain it.

Using the best set of parameters for each window size, we registered the
achieved RMS against the values of the target grid and the time needed to fit
the sources coefficients (see Fig.~\ref{fig:gradient-boosted-window-size}a).
In order to avoid any errors introduced by the way windows are shuffled, the
RMS for each window size was obtained as the mean RMS achieved by using
different random seeds.

We have also registered the computational time needed to fit the
gradient-boosted equivalent sources for each window size and computed the ratio
between these times and the computational time needed to fit the non-boosted
equivalent sources (see Fig.~\ref{fig:gradient-boosted-window-size}b).

\begin{figure}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-window-size.pdf}
    \caption{
        Gradient-boosted equivalent sources performance against window size.
        Window sizes are given as a fraction of the dimensions of the synthetic
        survey area.
        (a)~Root-mean-squared error between predictions and target grid using
        non-boosted sources (orange dashed line) and gradient-boosted
        equivalent sources (blue dots) for different window sizes. Each RMS
        error is the mean of the RMS produced by the same set of parameters but
        with different random seeds.
        (b)~Ratio between the computational times needed to fit the
        gradient-boosted and the non-boosted equivalent sources, respectively
        (the fitting time ratio for the non-boosted equivalent sources is
        therefore equal to one).
}
    \label{fig:gradient-boosted-window-size}
\end{figure}

From the results obtained from the comparison with the synthetic airborne
survey we can conclude that smaller windows generate less accurate predictions
than using larger ones and require significantly more computational time to fit
the sources.
The reduction of the accuracy might be due to an oversimplification of the
least-squares problem, and the increase of the computational time might be
generated by the great number of iterations required to fit the sources.
As the windows gets larger, the accuracy starts increasing because more data
points are included into the fitting process of the source coefficients, while
the fitting process takes less time due to a reduction of the number of
iterations.
For very large windows, both accuracy and fitting time are almost constant.

In comparison with the non-boosted equivalent sources, we can see that the
gradient-boosted ones produce slightly less accurate results due to not being
able to achieve the global minimum of the least-squares problem, but they
perform faster.

When using gradient-boosted equivalent sources we can conclude that we want to
maximize the window size as much as possible.
The only limitation to do so is to generate Jacobian matrices larger than the
available memory.
Therefore we recommend using the largest window that generates Jacobian
matrices that could fit in the available memory.

\subsection{Amount of overlap}

@@

We have also computed the fitting time ratio for each overlap, in a similar way
we did for the window sizes (see Fig.~\ref{fig:gradient-boosted-overlap}b).

\begin{figure}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-overlap.pdf}
    \caption{
        Gradient-boosted equivalent sources performance against amount of
        overlap.
        (a)~Root-mean-squared error between predictions and target grid using
        non-boosted sources (orange dashed line) and gradient-boosted
        equivalent sources (blue dots) for different amount of overlap. Each
        RMS error is the mean of the RMS produced by the same set of parameters
        but with different random seeds.
        (b)~Ratio between the computational times needed to fit the
        gradient-boosted and the non-boosted equivalent sources, respectively
        (the fitting time ratio for the non-boosted equivalent sources is
        therefore equal to one).
    }
    \label{fig:gradient-boosted-overlap}
\end{figure}

@@

@@

\section{Gridding gravity data from Australia}

@@

This section will demonstrate how gradient-boosted equivalent sources can be
used to interpolate large datasets of gravity data onto a regular grid at
uniform height.
For this purpose, we selected a compilation of ground gravity surveys over
Australia made by \citet{wynne2018} (TODO: MENTION THE COMPGEOLAB VERSION?).
It contains over 1.7 million data points and covers most of the Australian
territory at variable point spacings.
We computed the gravity disturbance by removing the normal gravity of the WGS84
ellipsoid from the observed gravity data (Fig.~\ref{fig:australia}).
Here, normal gravity was computed at each observation point through the
closed-form formula of \citet{ligotze2001} (TODO: ADD CITATION TO BOULE).
Finally, we convert the observations to planar Cartesian coordinates by
applying a Mercator projection.

We start the interpolation process by defining a set of block-averaged sources
at a relative depth of \AustraliaEqlDepth{} and a block size of
\SI{1.8}{\kilo\meter}, resulting in a total of \AustraliaEqlNSources{}~point
sources.
The block size was chosen to match the desired
resolution of the final grid.
In this case we will generate a regular grid with a resolution of 1~arc-minute,
which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.

@@

FOR DISCUSSION:

If the grid will have a much higher resolution than the block spacing, the
equivalent sources will not be able to reproduce the high frequency components
of the data.
Therefore we recommend setting a block spacing that matches the resolution of
the final grid.

@@

We are indebted to the developers and maintainers of the open-source software
without which this work would not have been possible.

The synthetic airborne survey was based upon the Great Britain aeromagnetic
data, reproduced with the permission of the British Geological Survey
$\textcopyright$UKRI\@.
All rights reserved.
